Sparsity Weak Lensing $3$-D Density Map Reconstruction: Reducing the line of sight smearing

### 2020-12-02 doc/paper_ms_method_HSCY1/ms.tex
add detection vs thresholds(post-construction)

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
Reducing the line of sight smearing.}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from
photometric weak-lensing shear measurements. The $3$-D density contrast maps
are modeled as a summation of the NFW basis atoms, which have $2$-D multi-scale
NFW surface density profiles on the transverse plane and $1$-D Dirac delta
functions in the line of sight direction. With the prior assumption that the
density fields have a sparse spatial distribution, the density fields are
reconstructed using an oracle algorithm: adaptive lasso. Our method is tested
with realistic simulations using the HSC-like shape estimation error and
photo-$z$ uncertainty.  Our findings are summarized as follows: 1) The lasso
solution suffers from a smear of structure in the line of sight direction even
in the absence of shape noise. The adaptive lasso algorithm significantly
removes the line of sight smear of structure.  2) The algorithm is able to
detect halo with minimal mass limits of $10^{13.5} M_{\odot}/h$, $10^{14.3}
M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq
z< 0.6$) and high ($0.6\leq z< 0.9$) redshifts, respectively.  3) The estimated
redshift of the halos detected from the reconstructed mass maps are lower than
the true redshift by about $0.03$ for halos at low redshifts ($z\leq 0.4$). The
relative redshift bias is below $0.5\%$ for halos at $0.4<z\leq 0.85$.
\end{abstract}

@@

\begin{figure*}[!t] \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
    \caption{The smoothed pixelized basis atoms. The upper row shows the basis
        atoms in Fourier space, and the lower row shows the basis atoms in Real
        space.  The leftmost column is the point mass atom, and the other
        columns are the multi-scale NFW atoms.  The smoothing kernel is
        Gaussian with a standard dev
        iation of $1.5$ pixels.
        } \label{fig-atoms2D}
\end{figure*}

\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
    \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
        corresponding $2$-D profiles are shown in Figure \ref{fig-atoms2D}.
        }
 \label{fig-atoms1D}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to
         their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
         blue histogram is the normalized number distribution of the best photo-$z$
         estimation. The vertical dashed lines are the boundaries of the redshift bins.
         The galaxies are equal-number binned.
        } \label{fig-bestpz}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
 \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
        }\label{fig-pdfpz}
\end{figure}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.\textwidth]{lensing_kernel.pdf}
 \caption{The left panel shows the lensing kernels for five different lens
         redshifts. The dashed lines are the kernels for spectroscopic redshift,
         which assumes that the source galaxies' redshifts are precisely
         estimated. The solid lines are for photometric redshifts, which
         accounts for the influence of photometric redshift uncertainty. The
         other two panels show the correlation between lensing kernels of
         different lens redshifts. The middle panel is for spectroscopic
         redshift, and the right panel is for photometric redshifts. The
         lensing kernels are normalized so that the diagonal elements of the
         correlation matrices equal one.
        }\label{fig-corlensKer}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
\caption{The density map reconstructions with the lasso (left) and the adaptive
        lasso (right) algorithms. The input density map is from a NFW halo with
        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
        reconstruction smears the density field along the line of sight
        direction (vertical direction in the plots).  The vertical direction is
        the line of sight direction, and the lower boundaries and upper
        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
        on galaxy shape measurements are neglected in this simulation.
        } \label{fig-lassoVsadaLasso}
\end{figure*}

@@

The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
transverse plane are shown in Figure \ref{fig-atoms2D}. The $1$-D slices of the
profiles are demonstrated in Figure \ref{fig-atoms1D}. Note that these profiles
are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
smoothing operation is discussed in Section \ref{subsec:method-smoothing}, and
the pixelization operation is discussed in Section \ref{subsec:method-pixel}.

@@

Figure \ref{fig-bestpz} shows the histogram of the best Machine Learning and
photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation from
\cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release
\citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins
according to the photo-$z$ best estimation, and the boundaries of the bins are
shown as vertical dashed lines in Figure \ref{fig-bestpz}. Figure \ref{fig-pdfpz}
shows the average probability density function (PDF) for galaxies in each
redshift bin.

The left panel of Figure \ref{fig-corlensKer} shows the lensing kernels for
lenses at five different redshifts as functions of source galaxy redshift bins.
The dashed lines are the lensing kernel for spectroscopic redshifts with
neglectable redshift uncertainty. The solid lines are the lensing kernel for
photometric redshifts with redshift uncertainties shown in Figure
\ref{fig-pdfpz}.  As shown by the dashed lines in the left panel of Figure
\ref{fig-corlensKer}, the lensing kernels converge to zero for source redshifts
lower than the lens redshift if the uncertainties on the source galaxy
redshift estimations are neglectable. However, as demonstrated by the solid
lines in the same panel, for the source redshifts with large photo-$z$
uncertainties, the lensing kernels do not converge to zero at redshifts lower
than the lens redshift. This is because the galaxies with photo-$z$ estimations
lower than the lens redshifts may be actually located at higher redshifts due
to the photo-$z$ uncertainties.

The middle and right panels show the correlation between lensing kernels for
lenses at different redshifts. The middle panel is for spect-$z$, and the right
panel is for photo-$z$.  As demonstrated in the middle panel, the lensing
kernels are highly correlated even though the redshift estimation is precise.
Comparing the correlation matrices shown in the middle panel and the right
panel of Figure \ref{fig-corlensKer}, we conclude that the photo-$z$
uncertainties further increase the correlations between lensing kernels at
different lens plane.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{The histograms of the HSC-like shape measurement error (including
         both from shape noise and from photon noise) on the first component of
         shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange
         lines). The solid steps are the sampled histograms, and the dashed
         lines are the normalized Gaussian distributions that have the same
         standard deviations as the corresponding histograms.
        }
 \label{fig-noiseHistogram}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.45\textwidth]{noise_std_map_pix.pdf}
 \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin
        ($0.69 \leq z < 0.80 $).
        } \label{fig-noistdmap}
\end{figure}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked $2$-D distribution of the deviations
     of detected peak positions from the centers of the corresponding input
     halos. The $x$-axis is for the deviated distance in the transverse plane,
     and the $y$-axis is for the deviation of the redshift. For each
     simulation, the positive peak inside the dashed black box with the
     minimal offset (in the pixel unit) from the input halo's position is
     taken as a true detection. The right panel focuses on the deviation of
     detected peaks in the line of sight direction. The $x$-axis is the input
     halo redshifts, and the $y$-axis is the redshift of the detected peak. The
     `$\cross$' denotes the average redshift of detected peaks for each halo
     over different noise realizations, and the error-bars are the
     uncertainties of the average redshifts. The deep gray area is for the
     relative redshift bias less than $0.05$, and the light gray area is for
     the relative redshift bias less than $0.5$. These results in this figure
     are based on the NFW dictionary with $\lambda=3.5$.
     } \label{fig-detoffsets}
\end{figure*}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
 \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peaks per square degree for mass map reconstructed with the NFW atoms. The
     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
     low panels show the results for $\lambda=5.0$.
        } \label{fig-detFalsRateNFW}
\end{figure*}

We pixelize the smoothed shear field into an $N_\theta \times N_\theta \times
N_s$ grid, where $N_\theta$ is the number of pixels for the two orthogonal axes
of the transverse plane and $N_s$ is the number of pixels for the line of sight
axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the
pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
N_s$. The grids on the transverse planes are equally spaced with a pixel size of
$1\arcmin$.  Fast Fourier transform (FFT) can be used to boost the speed of
linear operation on the transverse plane, whereas the grids in the line of sight
direction follow equal number binning as shown in Figure \ref{fig-bestpz}.

@@

The lasso algorithm selects the parameters relevant to the measurements and
simultaneously estimates the value of the selected parameters.  However, it has
been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
select the relevant parameters from the parameter space consistently.
Moreover, the estimated parameters are biased due to the shrinkage in the lasso
regression. We note that, for the density map reconstruction problem, the
column vectors are highly correlated even in the absence of photometric
redshift uncertainties because, as shown in Figure \ref{fig-corlensKer}, the
lensing kernels for lenses at different redshifts are highly correlated.
Therefore, the lasso algorithm cannot select the consistent mass in the line of
sight direction, and the reconstructed mass suffers from smears in the line of
sight direction even in the absence of noise on shear measurements.  Figure
\ref{fig-lassoVsadaLasso} shows the reconstructions of a single halo's mass map
with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
The noises on shear measurements are not included in the simulation.  The left
panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with the lasso
algorithm, which shows a significant smear along the line of sight.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values from all of the simulations.
     The solid lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed lines are the corresponding
     results of reconstructions from pure noise fields.
    }\label{fig-peakHist}
 \includegraphics[width=0.45\textwidth]{detfalse_threshold.pdf}
 \caption{Number of detections for true peaks (solid lines) and false
     peaks (dashed lines) as functions of selection thresholds.
     The lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$.
    }\label{fig-detfalse_threshold}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
        } \label{fig-NFWvsPM}
\end{figure*}

@@

The galaxy catalogs are simulated using the HSC S16A shape catalog
\citep{HSC1-catalog}.  We use galaxies in a one square degree region at the
center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
to have a homogeneous distribution statistically in the one-square
degree stamp. We randomly assign its redshift for each galaxy following the
MLZ photo-$z$ probability distribution function from By randomly rotating the
galaxies in the shape catalog, we simulate the HSC-like shape estimation error
with different realizations.  The histogram of the first component of the
HSC-like shape estimation error on galaxy level is shown in Figure
\ref{fig-noiseHistogram}.  The corresponding histogram of the shape error on
the pixel level after smoothing and pixelization is also shown in
\ref{fig-noiseHistogram}, and the standard deviation map of the noise is
demonstrated in Figure \ref{fig-noistdmap}.  \citep{HSC1-photoz}.

@@

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
 \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peak per square degree for mass map reconstructed with the point mass
     dictionary. The penalization paramter is set to $\lambda=3.5$ for the
     upper panels.  The lower panels show the results for $\lambda=5.0$.
        }\label{fig-detFalsRatePM}
\end{figure*}

@@

We detect the peaks on the density map after the reconstruction. The stacked
$2$-D histogram, from all of the simulations, for the offsets of the detected
peak positions from the input halos' positions is shown in the left panel of
Figure \ref{fig-detoffsets}.

For each simulation, we find the positive peak closest to the input position
(in the pixel unit), and if the closest peak lay inside the region denoted with
the dashed box in the left panel of Figure \ref{fig-detoffsets}, we take it as
a true peak detection of the input halo. Other detected peaks, which include both
positive and negative peaks, are taken as false peaks. The right
panel of Figure \ref{fig-detoffsets} shows the average redshift of true
detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.

Figure \ref{fig-peakHist} shows the histograms, which are normalized by the
number of simulations, for all detected peaks with different penalization
parameters. We also plot the corresponding histograms for peaks detected from
pure noise fields for comparison. From the left panels of Figure
\ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
peaks significantly decreases as the penalization parameter increases.

We note that when detecting galaxy clusters from the weak lensing mass maps in
real observations\citep{HSC1-massMap-cluster}, peaks greater than an ad-hoc
threshold is chosen as galaxy cluster candidates to suppress the number of
false detection. Figure \ref{fig-detfalse_threshold} shows the numbers of true
detections and false detections as functions of detection thresholds.

@@

>>>>

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
Reducing the line of sight smearing}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from
photometric weak-lensing shear measurements. The $3$-D density contrast maps
are modeled as a summation of the NFW basis atoms, which have $2$-D multi-scale
NFW surface density profiles on the transverse plane and $1$-D Dirac delta
functions in the line of sight direction. With the prior assumption that the
density fields have a sparse spatial distribution, the density fields are
reconstructed using an oracle algorithm: adaptive lasso. Our method is tested
with realistic simulations using the HSC-like shape estimation error and
photo-$z$ uncertainty.  Our findings are summarized as follows: 1) The lasso
solution suffers from a smear of structure in the line of sight direction even
in the absence of shape noise. The adaptive lasso algorithm significantly
removes the line of sight smear of structure.  2) The algorithm is able to
detect halo with minimal mass limits of $10^{14.0} M_{\odot}/h$, $10^{14.7}
M_{\odot}/h$, $10^{15.0} M_{\odot}/h$ for the low ($z<0.3$), median ($0.3\leq
z< 0.6$) and high ($0.6\leq z< 0.85$) redshifts, respectively, with a false
detection of 0.022/deg$^2$.  3) The estimated redshift of the halos detected
from the reconstructed mass maps are lower than the true redshift by about
$0.03$ for halos at low redshifts ($z\leq 0.4$). The relative redshift bias is
below $0.5\%$ for halos at $0.4<z\leq 0.85$.
\end{abstract}

@@

\begin{figure*}[!t] \includegraphics[width=1.\textwidth]{nfwlet-atom-2D.pdf}
    \caption{The smoothed pixelized basis atoms. The upper row shows the basis
        atoms in Fourier space, and the lower row shows the basis atoms in Real
        space.  The leftmost column is the point mass atom, and the other
        columns are the multi-scale NFW atoms.  The smoothing kernel is
        Gaussian with a standard dev
        iation of $1.5$ pixels.
        } \label{fig_atoms2D}
\end{figure*}

\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
    \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
        corresponding $2$-D profiles are shown in Figure \ref{fig_atoms2D}.
        }
 \label{fig_atoms1D}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to
     their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
     blue histogram is the normalized number distribution of the best photo-$z$
     estimation. The vertical dashed lines are the boundaries of the redshift
     bins.  The galaxies are equal-number binned.
        } \label{fig_bestpz}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
 \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
        }\label{fig_pdfpz}
\end{figure}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.\textwidth]{lensing_kernel.pdf}
 \caption{The left panel shows the lensing kernels for five different lens
         redshifts. The dashed lines are the kernels for spectroscopic redshift,
         which assumes that the source galaxies' redshifts are precisely
         estimated. The solid lines are for photometric redshifts, which
         accounts for the influence of photometric redshift uncertainty. The
         other two panels show the correlation between lensing kernels of
         different lens redshifts. The middle panel is for spectroscopic
         redshift, and the right panel is for photometric redshifts. The
         lensing kernels are normalized so that the diagonal elements of the
         correlation matrices equal one.
        }\label{fig_corlensKer}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
\caption{The density map reconstructions with the lasso (left) and the adaptive
        lasso (right) algorithms. The input density map is from a NFW halo with
        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
        reconstruction smears the density field along the line of sight
        direction (vertical direction in the plots).  The vertical direction is
        the line of sight direction, and the lower boundaries and upper
        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
        on galaxy shape measurements are neglected in this simulation.
        } \label{fig_lassoVsadaLasso}
\end{figure*}

@@

The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
smoothing operation is discussed in Section \ref{subsec:method-smoothing}, and
the pixelization operation is discussed in Section \ref{subsec:method-pixel}.

@@

Figure \ref{fig_bestpz} shows the histogram of the best Machine Learning and
photo-Z \citep[MLZ]{MLZ-TPZ2013} photometric redshift estimation from
\cite{HSC1-photoz} for galaxies in the tract 9347 of the HSC S16A data release
\citep{HSC1-data}. These Galaxies are divided into ten source galaxy bins
according to the photo-$z$ best estimation, and the boundaries of the bins are
shown as vertical dashed lines in Figure \ref{fig_bestpz}. Figure \ref{fig_pdfpz}
shows the average probability density function (PDF) for galaxies in each
redshift bin.

The left panel of Figure \ref{fig_corlensKer} shows the lensing kernels for
lenses at five different redshifts as functions of source galaxy redshift bins.
The dashed lines are the lensing kernel for spectroscopic redshifts with
neglectable redshift uncertainty. The solid lines are the lensing kernel for
photometric redshifts with redshift uncertainties shown in Figure
\ref{fig_pdfpz}.  As shown by the dashed lines in the left panel of Figure
\ref{fig_corlensKer}, the lensing kernels converge to zero for source redshifts
lower than the lens redshift if the uncertainties on the source galaxy
redshift estimations are neglectable. However, as demonstrated by the solid
lines in the same panel, for the source redshifts with large photo-$z$
uncertainties, the lensing kernels do not converge to zero at redshifts lower
than the lens redshift. This is because the galaxies with photo-$z$ estimations
lower than the lens redshifts may be actually located at higher redshifts due
to the photo-$z$ uncertainties.

The middle and right panels show the correlation between lensing kernels for
lenses at different redshifts. The middle panel is for spect-$z$, and the right
panel is for photo-$z$.  As demonstrated in the middle panel, the lensing
kernels are highly correlated even though the redshift estimation is precise.
Comparing the correlation matrices shown in the middle panel and the right
panel of Figure \ref{fig_corlensKer}, we conclude that the photo-$z$
uncertainties further increase the correlations between lensing kernels at
different lens plane.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{The histograms of the HSC-like shape measurement error (including
         both from shape noise and from photon noise) on the first component of
         shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange
         lines). The solid steps are the sampled histograms, and the dashed
         lines are the normalized Gaussian distributions that have the same
         standard deviations as the corresponding histograms.
        }
 \label{fig_noiseHistogram}
\end{figure}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{noise_std_map_pix.pdf}
 \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin
        ($0.69 \leq z < 0.80 $).
        } \label{fig_noistdmap}
\end{figure}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.0\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked $2$-D distribution of the deviations
     of detected peak positions from the centers of the corresponding input
     halos. The $x$-axis is for the deviated distance in the transverse plane,
     and the $y$-axis is for the deviation of the redshift. For each
     simulation, the positive peak inside the dashed black box with the
     minimal offset (in the pixel unit) from the input halo's position is
     taken as a true detection. The right panel focuses on the deviation of
     detected peaks in the line of sight direction. The $x$-axis is the input
     halo redshifts, and the $y$-axis is the redshift of the detected peak. The
     `$\cross$' denotes the average redshift of detected peaks for each halo
     over different noise realizations, and the error-bars are the
     uncertainties of the average redshifts. The deep gray area is for the
     relative redshift bias less than $0.05$, and the light gray area is for
     the relative redshift bias less than $0.5$. These results in this figure
     are based on the NFW dictionary with $\lambda=3.5$.
     } \label{fig_detoffsets}
\end{figure*}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.0\textwidth]{detfalseRate_f3-1.pdf}
 \includegraphics[width=1.0\textwidth]{detfalseRate_f3-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peaks per square degree for mass map reconstructed with the NFW atoms. The
     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
     low panels show the results for $\lambda=5.0$.
        } \label{fig_detFalsRateNFW}
\end{figure*}

We pixelize the smoothed shear field into an $N_\theta \times N_\theta \times
N_s$ grid, where $N_\theta$ is the number of pixels for the two orthogonal axes
of the transverse plane and $N_s$ is the number of pixels for the line of sight
axis. $\gamma_{\alpha}$ denotes the smoothed shear measurements recorded on the
pixel with index $\alpha$, where $\alpha=1...N_\theta \times N_\theta \times
N_s$. The grids on the transverse planes are equally spaced with a pixel size of
$1\arcmin$.  Fast Fourier transform (FFT) can be used to boost the speed of
linear operation on the transverse plane, whereas the grids in the line of sight
direction follow equal number binning as shown in Figure \ref{fig_bestpz}.

@@

The lasso algorithm selects the parameters relevant to the measurements and
simultaneously estimates the value of the selected parameters.  However, it has
been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
select the relevant parameters from the parameter space consistently.
Moreover, the estimated parameters are biased due to the shrinkage in the lasso
regression. We note that, for the density map reconstruction problem, the
column vectors are highly correlated even in the absence of photometric
redshift uncertainties because, as shown in Figure \ref{fig_corlensKer}, the
lensing kernels for lenses at different redshifts are highly correlated.
Therefore, the lasso algorithm cannot select the consistent mass in the line of
sight direction, and the reconstructed mass suffers from smears in the line of
sight direction even in the absence of noise on shear measurements.  Figure
\ref{fig_lassoVsadaLasso} shows the reconstructions of a single halo's mass map
with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
The noises on shear measurements are not included in the simulation.  The left
panel of Figure \ref{fig_lassoVsadaLasso} is the reconstruction with the lasso
algorithm, which shows a significant smear along the line of sight.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values from all of the simulations.
     The solid lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed lines are the corresponding
     results of reconstructions from pure noise fields.
    }\label{fig_peakHist}
\end{figure}

@@

\begin{figure*}[!t]
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
        } \label{fig_NFWvsPM}
\end{figure*}

@@

The galaxy catalogs are simulated using the HSC S16A shape catalog
\citep{HSC1-catalog}.  We use galaxies in a one square degree region at the
center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
to have a homogeneous distribution statistically in the one-square
degree stamp. We randomly assign its redshift for each galaxy following the
MLZ photo-$z$ probability distribution function from By randomly rotating the
galaxies in the shape catalog, we simulate the HSC-like shape estimation error
with different realizations.  The histogram of the first component of the
HSC-like shape estimation error on galaxy level is shown in Figure
\ref{fig_noiseHistogram}.  The corresponding histogram of the shape error on
the pixel level after smoothing and pixelization is also shown in
\ref{fig_noiseHistogram}, and the standard deviation map of the noise is
demonstrated in Figure \ref{fig_noistdmap}.  \citep{HSC1-photoz}.

@@

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=1.0\textwidth]{detfalseRate_f1-1.pdf}
 \includegraphics[width=1.0\textwidth]{detfalseRate_f1-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peak per square degree for mass map reconstructed with the point mass
     dictionary. The penalization paramter is set to $\lambda=3.5$ for the
     upper panels.  The lower panels show the results for $\lambda=5.0$.
        }\label{fig_detFalsRatePM}
\end{figure*}

@@

We detect the peaks on the density map after the reconstruction. The stacked
$2$-D histogram, from all of the simulations, for the offsets of the detected
peak positions from the input halos' positions is shown in the left panel of
Figure \ref{fig_detoffsets}.

For each simulation, we find the positive peak closest to the input position
(in the pixel unit), and if the closest peak lay inside the region denoted with
the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
a true peak detection of the input halo. Other detected peaks, which include both
positive and negative peaks, are taken as false peaks. The right
panel of Figure \ref{fig_detoffsets} shows the average redshift of true
detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.

Figure \ref{fig_peakHist} shows the histograms, which are normalized by the
number of simulations, for all detected peaks with different penalization
parameters. We also plot the corresponding histograms for peaks detected from
pure noise fields for comparison. From the left panels of Figure
\ref{fig_NFWvsPM}, which show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
peaks significantly decreases as the penalization parameter increases.

@@

\begin{figure*}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold.pdf}
 \caption{The left panel and the middle panel show the halo detection rates
     with different input masses and redshifts. The detections are performed on
     the mass maps reconstructed with $\lambda=5.0$, and the detection
     thresholds are set to $1.5\sigma$ and $3.0\sigma$ of the peak's standard
     deviation of the noise field, respectively. The right panel shows the
     numbers of false peaks per square degree as a function of selection
     thresholds. The corresponding false peaks per square degree for thresholds
     of $1.5\sigma$ and $3.0\sigma$ are about $0.022~\rm{deg}^{-2}$ and
     $0.004~\rm{deg}^{-2}$.
    }\label{fig_detfalse_threshold}
\end{figure*}
